---
title: "R Bridge Final Project"
author: "Sam CD"
date: "November 29, 2015"
output: html_document
---

This projects uses the **Hflights** package by Hadley Wickham, available at:
<https://cran.r-project.org/web/packages/hflights/hflights.pdf>.
 or by running

```{r,echo=TRUE}
install.packages("hflights")
library("hflights")
```

I wanted to compare two variables, Distance and Arrival Time, so I took only those two columns:

```{r, echo=TRUE}
dist_delay <- hflights[c("Distance","ArrDelay")]
```

Specifically, I wanted to divide into flights that arrive early, late or on-time:
```{r,echo=TRUE}
late <- subset(dist_delay,ArrDelay > 0)
early <- subset(dist_delay,ArrDelay < 0)
onTime <- subset(dist_delay,ArrDelay = 0)
```

to answer the question "Is a long-distance flight likely to cause a delay?"

A correlation matrix appears to show a very slight negative correlation
```{r,echo=FALSE}
cor(dist_delay,use = "complete.obs")
```

The density plots for all three scenarios appear very similar
```{r,echo=FALSE}
plot(density(late$Distance))
plot(density(early$Distance))
plot(density(onTime$Distance))
```

and the mean and median distances of each subset are very close
```{r,echo=FALSE}
summary(dist_delay)
summary(late)
summary(early)
summary(onTime)
```

but a Two Sample t-test does show a steady difference in means
```{r,echo=FALSE}
t.test(early,late)
```

all leading me to the conclusion that, while there is a slight negative correlation between the two, meaning a longer distance would cause a greater delay, there does not seem to be any other supporting statistics or graphics to be able to draw this conclusion.
